New lower bounds for Schur and weak Schur numbers

### 2021-04-17 article/schur.tex
conclusion schur

\subsection{Conclusion on SF-templates}

>>>>

\subsection{Conclusion on SF-templates}
In this section, we first formalized the Rowley's template-based constructions \cite{RowleyRamsey} by introducing SF-templates. In order to formalize the construction, we then defined a new number, \(S^+\), and demonstrated a relation between \(S^+\) and \(S\). We found lower bounds for \(S^+\) and that allowed us to obtain new lower bounds for schur numbers. One may notice that we only get lower bounds of \(S^+\) and as a result it should be possible to find a better templates by constraining less the search space. In the next section, we will introduce \(WS^+\) and deduce a relation that improve lower bounds for weak-schur numbers by analogy with this section.
